Long-term care homes were hit hardest by 2023 disease outbreaks in Toronto healthcare facilities

### 2024-01-22 outputs/paper/paper.qmd
Added average age of long-term care home residents

All three of these results share common origins. For instance, in October 2022, the Government of Ontario removed a masking requirement for caregivers and visitors in long-term care homes [@cbcltch], whose residents are primarily at or above 65 years of age as reported in 2018 [@clri]. Since individuals aged 60 years or older are more likely to experience worse health effects after contracting COVID-19, the Public Health Agency of Canada recommends that they wear a respirator or mask to limit the transmission of this pathogen [@phaccovid]. As a result, it seems that the Government of Ontario did not heed this advice, possibly contributing to the large proportion of disease outbreaks (which include COVID-19) in Toronto long-term care homes in 2023. This appears to follow a long-standing trend in Ontario long-term care homes. For example, at the start of the COVID-19 pandemic, long-term care homes in Ontario experienced a sizable increase in COVID-19 cases [@cbcinquiry]. This was potentially made worse by the fact that not all of these facilities enforced mask-wearing and that long-term care homes were passed over for personal protective equipment in favour of hospitals [@cbcinquiry]. Moreover, the fact that several hospitals in Toronto curtailed their mask requirements in June and July of 2023 [@hospitalmasks] likely contributed to the large volume of respiratory disease outbreaks observed in @tbl-outbreaks-by-outbreak-type and @fig-outbreaks-by-outbreak-type.

>>>>

All three of these results share common origins. For instance, in October 2022, the Government of Ontario removed a masking requirement for caregivers and visitors in long-term care homes [@cbcltch], whose residents are primarily at or above 65 years of age with an average age of 83 years as reported in 2018 [@clri]. Since individuals aged 60 years or older are more likely to experience worse health effects after contracting COVID-19, the Public Health Agency of Canada recommends that they wear a respirator or mask to limit the transmission of this pathogen [@phaccovid]. As a result, it seems that the Government of Ontario did not heed this advice, possibly contributing to the large proportion of disease outbreaks (which include COVID-19) in Toronto long-term care homes in 2023. This appears to follow a long-standing trend in Ontario long-term care homes. For example, at the start of the COVID-19 pandemic, long-term care homes in Ontario experienced a sizable increase in COVID-19 cases [@cbcinquiry]. This was potentially made worse by the fact that not all of these facilities enforced mask-wearing and that long-term care homes were passed over for personal protective equipment in favour of hospitals [@cbcinquiry]. Moreover, the fact that several hospitals in Toronto curtailed their mask requirements in June and July of 2023 [@hospitalmasks] likely contributed to the large volume of respiratory disease outbreaks observed in @tbl-outbreaks-by-outbreak-type and @fig-outbreaks-by-outbreak-type.
